---
title: "Introduction of R package moonBook2(4)"
author: "Keon-Woong Moon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Package installation

Package `moonBook` is avaiable on CRAN and github. Package `moonBook2` is available only on github. Please install moonBook2 package using the following R code.

```{r,eval=FALSE}
install.packages("devtools")
devtools::install_github("cardiomoon/moonBook")
devtools::install_github("cardiomoon/moonBook2")
```

In this vignette, I will show you how to make a choropleth map with moonBook2 package.

1. ggChoropleth() make a choropleth map with moonBook2 package.
2. ggErrorbar() make a bar plot with errorbars

## ggChoropleth()

A choropleth map is a map with regions that are colored according to variable values. To make a choropleth map, two data is required. One is the map data. The other is data for colors.
For example, you can get the map data of Unites States by using the following code.
```{r,message=FALSE,comment=NA}
require(ggplot2)
require(moonBook2)
require(ggiraph)
states_map <- map_data("state")
```

You can make a US crime data by following code.
```{r,message=FALSE,comment=NA}
crimes <- data.frame(state = tolower(rownames(USArrests)), USArrests)
crimes
```

Because the states are coded in lower cases in  states_map, you have to use lower case in you data. You can make a choropleth map showing the `murder` rate easily by the following code.

```{r,message=FALSE,warning=FALSE,comment=NA,fig.width=7,fig.height=5}
ggChoropleth(crimes,states_map,fill="Murder",map_id="state",interactive=TRUE)
```

You can make a choropleth map with different colors.
```{r,message=FALSE,warning=FALSE,comment=NA,fig.width=7,fig.height=7}
ggChoropleth(crimes,states_map,fill="UrbanPop",map_id="state",
             colors=c('white','steelblue'),interactive=TRUE)
```

If you want to make a faceted choroplath map, you have to reshape your data into long form. For example, the crimes data can be reshaped to a long form by the following R code.

```{r,message=FALSE,warning=FALSE,comment=NA,fig.width=7,fig.height=7}
crimeslong=reshape2::melt(crimes,id="state")
str(crimeslong)
```

And then you can make static ggplot with ggChoropleth() function first and then add the facets by facet_wrap function nad finally call ggiraph() function to draw a interactive map.
```{r,message=FALSE,warning=FALSE,comment=NA,fig.width=5,fig.height=5}
p<-ggChoropleth(crimeslong,states_map,fill="value",map_id="state",
             colors=c('white','green','steelblue','red'))
p<-p+facet_wrap(~variable)
ggiraph(code=print(p))
```

## ggErrorBar()

You can make barplot with errobars easliy with ggErrorBar(). With Salaries data, you can summarize the salary of professors with mean and se/sd and draw a bar plot with errorbar.

```{r}
require(car)  # for use of data Salaries
ggErrorBar(Salaries,yvar="salary",xvar="rank",group="sex",interactive=TRUE)
```

By default, the error bar is displayed two-sided. You can display errorbar one-side only by change the mode=1.
```{r}
require(moonBook)  # for use of data acs
ggErrorBar(acs,"age","Dx","sex",interactive=TRUE,mode=1)
ggErrorBar(acs,"age","Dx",interactive=TRUE,mode=1)
```

You can use ggErrorBar() function with formula.
```{r}
ggErrorBar(age~Dx*sex,data=acs,interactive=TRUE)
```

