---
title: "Introduction of moonBook2(1)"
author: "Keon-Woong Moon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package contains several functions make interactive plots with ggplot2 and ggiraph package.

## ggSpine() : Interactive mosaic plot and spinogram

This function is a extension of graphics::spineplot() function. This function draws a proportional stacked barplot with variable width. 

```{r,message=FALSE,comment=NA}
require(moonBook)
require(ggplot2)
require(ggiraph)
require(plyr)
require(reshape2)
require(scales)
require(moonBook2)

ggSpine(data=acs,"Dx","smoking",interactive=TRUE)
```

Like a bar plot, you can set the parameter position among "stack","dodge" and "fill". You can add labels by setting the parameter addlabel TRUE.
```{r,message=FALSE,comment=NA}
ggSpine(data=acs,"Dx","smoking",addlabel=TRUE,position="stack",interactive=TRUE)
ggSpine(data=acs,"Dx","smoking",addlabel=TRUE,position="dodge",interactive=TRUE)
```

When used with a continuous variable, it draws a spinogram which is an extension of histogram. In this case, the barwidth is set with a value 1.0(you can adjust the value).  

```{r,message=FALSE,comment=NA}
ggSpine(data=acs,Dx,age,addlabel=TRUE,interactive=TRUE)
```

You can draw a plot with pre-processed data. In this example, we use the rose data in moonBook2 package. You can assign a continuous variable(rose[["value"]]") to y-axis variable and set the parameter stat "identity".
```{r,message=FALSE,comment=NA}
head(rose,10)
ggSpine(rose,"group","Month",yvar="value",stat="identity",width=1,interactive=TRUE)
```

You can make a "Rose" plot with variable width.
```{r,message=FALSE,comment=NA}
ggSpine(rose,"group","Month",yvar="value",stat="identity",position="stack",width=1,
        polar=TRUE,interactive=TRUE,palette="Reds")
```

## ggRadar() : Interactive Radar chart

Radar chart is a graphical method of displaying three or more continuous data in a 2-dimensional chart. With moonBook::acs data, we can complare all continuous variables in patients with acute coronary syndrome.

```{r,message=FALSE,comment=NA}
ggRadar(acs,groupvar="sex",interactive=TRUE)
```

Because the distributions of variables are differ, you should rescle the data by set the parameter rescale TRUE.
```{r,message=FALSE,comment=NA}
ggRadar(acs,groupvar="sex",interactive=TRUE,rescale=TRUE)
```
As you can see, male patients are taller and heavier than female patients. But the bod mass index(BMI) is almost the same.

With mtcars data, you can make a exploratoty plot with this command. 

```{r,message=FALSE,comment=NA}
ggRadar(mtcars,groupvar="am",rescale=TRUE,interactive=TRUE)
ggRadar(mtcars,groupvar="cyl",rescale=TRUE,interactive=TRUE)
```

You can make faceted chart with this code.

```{r}
mtcars$model=rownames(mtcars)
p<-ggRadar(mtcars[1:9,],rescale=TRUE,groupvar="model",legend.position="none")+
         ylim(0,1)+facet_wrap(~model)
ggiraph(code=print(p))
```


## ggPieDonut() : Combine Pie and Donut plot

You can combine Pie and donut plot easily with ggPieDonut() function. Let's see the browsers data.

```{r,message=FALSE,comment=NA}
str(browsers)
```

With this data, you can make the PieDonut plot easily.
```{r,message=FALSE,comment=NA,warning=FALSE}
ggPieDonut(browsers,pies="browser",donuts="version",count="share",interactive=TRUE)
```

When with categrical variables, ggPieDonut() function calculate the count.
```{r,message=FALSE,comment=NA,warning=FALSE}
ggPieDonut(acs,"Dx","smoking",interactive=TRUE)
```
```{r,message=FALSE,comment=NA,warning=FALSE}
ggPieDonut(mtcars,"cyl","carb",labelposition=0,interactive=TRUE)
```
