---
title: "Introduction of R package moonBook2(3)"
author: "Keon-Woong Moon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Package installation

Package `moonBook` is avaiable on CRAN and github. Package `moonBook2` is available only on github. Please install moonBook2 package using the following R code.

```{r,eval=FALSE}
install.packages("devtools")
devtools::install_github("cardiomoon/moonBook")
devtools::install_github("cardiomoon/moonBook2")
```

In this vignette, I will show you how to visualize the interaction between two predictor variables. 

1. PopPyramid(): get population data from internet and make a population pyramid.
2. ggPoints(): make a scatterplot with/without regression line
3. ggBar(): make a interactive barplot
4. ggRose(): make a interactive Rose plot
5. ggHeatmap(): make a interactive Rose plot


## PopPyramid() for population pyramid

You can’t make a population pyramid without data; PopPyramid() function gets population data data from US Census Bereau. This function uses get_popdata() function internally and this function is a modification of get_data() function of [Kyle Walker's](https://rpubs.com/walkerke/pyramids_ggplot2). You can use PopPyramid function with the following format.

```
PopPyramid(country,year,interactive=FALSE)
```

The country parameter shoud be one of the [FIPS 10-4 country code](https://en.wikipedia.org/wiki/List_of_FIPS_country_codes). If you wnated to make a population pyramid 2016 for Nigeria, you can use the following code.

```{r,message=FALSE,warning=FALSE,comment=NA}
require(moonBook2)
require(ggplot2)
require(ggiraph)
require(moonBook)

PopPyramid("NI",2016,interactive=TRUE)
```
   
The followings are other examples.
```{r,message=FALSE,warning=FALSE,comment=NA}
PopPyramid("KS",2016,interactive=TRUE)  # for South Korea
PopPyramid("US",2016,interactive=TRUE)  # for United States
```


## ggPoints() for scatterplot


You can make interactive scatter plot by ggPoints(). You can make a scatterplot by two different ways.


### by using column name
```{r,message=FALSE,warning=FALSE,comment=NA,fig.width=5,fig.height=5}
require(plotly)
ggPoints(iris,Sepal.Width,Sepal.Length,interactive=TRUE)

```

You can assign a grouping variable to the colour or the fill parameter.

```{r,message=FALSE,warning=FALSE,comment=NA,fig.width=5,fig.height=5}
ggPoints(iris,Sepal.Width,Sepal.Length,colour="Species",interactive=TRUE )
```

You can remove the regression line by setting the smooth parameter 'FALSE'.
```{r,message=FALSE,warning=FALSE,comment=NA,fig.width=5,fig.height=5}
ggPoints(iris,Sepal.Width,Sepal.Length,colour="Species",smooth=FALSE,interactive=TRUE )
```

You can adjust the method of regression by setting the method from "auto" to other method and adjust the formula option with formula parameter.

```{r,message=FALSE,warning=FALSE,comment=NA,fig.width=5,fig.height=5}

ggPoints(mtcars,mpg,wt,colour="am",method="lm",formula="y~poly(x,2)",interactive=TRUE)
```

## by formula

You can use formula as follows.

```{r,message=FALSE,warning=FALSE,comment=NA,fig.width=5,fig.height=5}
ggPoints(mpg~wt,data=mtcars,interactive=TRUE )
ggPoints(mpg~wt|am,data=mtcars,interactive=TRUE )
```


For radial artery atherosclerosis data, you can draw scatter plot as follows.
```{r,message=FALSE,warning=FALSE,comment=NA,fig.width=5,fig.height=5}
require(car)
ggPoints(salary~yrs.service|sex,data=Salaries,method="lm",formula="y~poly(x,2)",interactive=TRUE )
```

If you wanted to add another layers or options, you can make a ggplot without interactive=TRUE(the default value of interactive is FALSE) and add option(s) to the ggplot. 

```{r,message=FALSE,warning=FALSE,comment=NA,fig.width=5,fig.height=5}
require(car)

p<-ggPoints(salary~yrs.service|sex,data=Salaries,method="lm",formula="y~poly(x,2)")
p<-p+facet_wrap(~sex)
p
ggplotly(p)
```

## ggBar() for easy interactive barplot

You can make interactive barplot by ggBar(). 

```{r}
ggBar(acs,"Dx","smoking",interactive=TRUE)
```

You can add labels to barplot easily by setting the parameter addlabel=TRUE
```{r}
ggBar(acs,"Dx","smoking",addlabel=TRUE,interactive=TRUE)
ggBar(acs,"Dx","smoking",position="dodge",addlabel=TRUE,interactive=TRUE)
ggBar(acs,"Dx","smoking",position="fill",addlabel=TRUE,interactive=TRUE)
```

You can make horizontal bar plot easily by setting the parameter horizontal=TRUE
````{r}
ggBar(acs,"Dx","smoking",position="fill",addlabel=TRUE,horizontal=TRUE,yangle=90,
      width=0.5,interactive=TRUE)
```

You can make polar map by setting the parameter polar=TRUE
```{r}
ggBar(acs,"Dx","smoking",interactive=TRUE,width=1,colour="white",size=0.2,polar=TRUE)
```

You can make barplot from preprocessed data.
```{r}
ggBar(rose,Month,group,"value",stat="identity",interactive=TRUE)
```


## ggRose() ; for interactive Rose plot

You can make rose plot by using ggBar().

```{r}
ggBar(rose,Month,group,"value",stat="identity",polar=TRUE,palette="Reds",width=1,
       color="black",size=0.1,interactive=TRUE)
```

You can make rose plot more easily by using ggRose()

```{r}
ggRose(rose,Month,group,"value",interactive=TRUE)
```

Here comes another example of ggRose().
```{r}
ggRose(acs,"Dx","smoking",interactive=TRUE)
```


##ggHeatmap() ; for easy interactive heatmap

In heatmap, you can assign a continuous variable to the `fill` color. You can make interactive heatmap by using ggHeatmap()

```{r}
ggHeatmap(acs,"Dx","smoking",interactive=TRUE)
```

You can add labels to heatmap easily by setting the parameter addlabel=TRUE
```{r}
ggHeatmap(acs,"Dx","smoking",addlabel=TRUE,interactive=TRUE)
```

You can make heatmap with preprocessed data.

```{r}
ggHeatmap(rose,"group","Month","value",stat="identity",interactive=TRUE)
```        
You can change the fill colors by seting the parameter gradient_colors() 
```{r}
ggHeatmap(rose,"group","Month","value",stat="identity",gradient_colors = c("white","red"),interactive=TRUE)
```

You can make polar heatmap by seting the parameter polar TRUE.
```{r}
ggHeatmap(rose,"Month","group","value",stat="identity",polar=TRUE,interactive=TRUE)
```

Another example comse from *taco* data. This data is made by "Aaron Richter". Please take a look at one of his wonderful post [Communicating Experimental Results with R](http://rikturr.com/blog/communicating-experimental-results-with-r/).


```{r,comment=NA}
head(taco)
str(taco)
```

This data consisits of ratings of taco by shell types, age groups and filllings. You can make heatmap with this data.

```{r}
ggHeatmap(taco,"AgeGroup","Filling","Rating",stat="identity",interactive=TRUE)
```

You add facets to you heatmap.
```{r}
ggHeatmap(taco,"AgeGroup","Filling","Rating",facetvar="ShellType",
          stat="identity",interactive=TRUE)
```
